---
title: "Multimedia Meta-analysis Scripts"
date: "Updated: `r format(Sys.Date(), format='%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    number_sections: no
---

<br/>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.retina = 4)
```

```{r}
# Libraries
pacman::p_load(metafor, readxl, MAd, metaforest, dmetar, DT, robumeta, janitor, tidyverse, texreg, effectsize, skimr)

# Parameters
data_file <- here::here("data", "Multimedia Meta Data.xlsx")

# effectsize::t_to_d(2.22, 139)
# dmetar::se.from.p(effect.size = 0.38, p = 0.028, N = 141) %>% transmute(EV = round(StandardError * StandardError, 4))
```



```{r}
#### Directly entered ES

df_es1 <-
  read_xlsx(data_file, sheet = "Effect Size Only 1") %>% 
  transmute(
    study_id = STUDYID,
    type = str_sub(Outcome, 1, 3),
    ES,
    EV
  ) %>% 
  remove_empty()

df_es2 <-
  read_xlsx(data_file, sheet = "Effect Size Only 2") %>% 
  remove_empty() %>% 
  transmute(
    study_id = STUDYID,
    type = str_sub(Outcome, 1, 3),
    ES,
    EV
  ) %>% 
  remove_empty()

  
df_es3 <-
  read_xlsx(data_file, sheet = "Effect Size Only 3") %>% 
  transmute(study_id = STUDYID, type = str_sub(Outcome, 1, 3), ES = ES1, EV = se1 * se1) %>%
  bind_rows(
    read_xlsx(data_file, sheet = "Effect Size Only 3") %>% 
      transmute(study_id = STUDYID, type = str_sub(Outcome, 1, 3), ES = ES2, EV = se2 * se2)
  )

df_es4 <-
  read_xlsx(data_file, sheet = "Effect Size Only 4") %>% 
  remove_empty() %>% 
  transmute(
    study_id = STUDYID,
    type = str_sub(Outcome, 1, 3),
    ES,
    EV
  ) %>% 
  remove_empty()

df_es5 <-
  read_xlsx(data_file, sheet = "Effect Size Only 5") %>% 
  remove_empty() %>% 
  transmute(
    study_id = STUDYID,
    type = str_sub(Outcome, 1, 3),
    ES,
    EV
  ) %>% 
  remove_empty()

df_es6 <-
  read_xlsx(data_file, sheet = "Effect Size Only 6") %>% 
  remove_empty() %>% 
  transmute(
    study_id = STUDYID,
    type,
    ES,
    EV
  ) %>% 
  remove_empty()

df_es_direct <-
  bind_rows(df_es1, df_es2, df_es3, df_es4, df_es5, df_es6) %>% 
  inner_join(
    read_xlsx(data_file, sheet = "All Studies") %>% 
      select(study_id = `STUDYID`, AUTYR = `Author (Year)`) %>% 
      drop_na(AUTYR),
    by = "study_id"
  )
```


```{r}
### Load all data

df_raw <-
  bind_rows(
    "DSN" = read_xlsx(data_file, sheet = "Decoding-DSN") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "DSN", "")),
    "DRD" = read_xlsx(data_file, sheet = "Decoding-DRD") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "DRD", "")),
    "DRP" = read_xlsx(data_file, sheet = "Decoding-DRP") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "DRP", "")),
    "LSN" = read_xlsx(data_file, sheet = "Linguistic Comprehension-LSN") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "LSN", "")),
    "LRD" = read_xlsx(data_file, sheet = "Linguistic Comprehension-LRD") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "LRD", "")),
    "LRP" = read_xlsx(data_file, sheet = "Linguistic Comprehension-LRP") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "LRP", "")),
    "CSN" = read_xlsx(data_file, sheet = "Reading Comprehension-CSN") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "CSN", "")),
    "CRD" = read_xlsx(data_file, sheet = "Reading Comprehension-CRD") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "CRD", "")),
    "WPSN" = read_xlsx(data_file, sheet = "Writing Proficiency-WPSN") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "WPSN", "")),
    "WPRD" = read_xlsx(data_file, sheet = "Writing Proficiency-WPRD") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "WPRD", "")),
    .id = "type"
  ) %>% 
  rename(study_id = `STUDYID`) %>%
  drop_na(study_id) %>%
  anti_join(df_es6, by = c("type", "study_id")) %>%
  bind_rows(
    .,
    bind_rows(
      "DSN" = read_xlsx(data_file, sheet = "New Postonly") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "DSN", "")),
      "DSN" = read_xlsx(data_file, sheet = "New Prepost") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "DSN", "")),
      # "LSN" = read_xlsx(data_file, sheet = "New Prepost 2") %>% rename_at(vars(-c(1:2)), ~ str_replace(., "LSN", "")),
      .id = "type"
    )
  ) %>%
  remove_empty() %>%
  select(-`Author (Year)`) %>% 
  select(study_id, type, sort(current_vars()))
```


```{r}
# HLM data

df_hlm1 <-
  read_xlsx(data_file, sheet = "HLM Effects 1") %>% 
  mutate(
    type = str_sub(Outcome, 1, 3),
    msr = str_sub(Outcome, 4, 4),
  ) %>% 
  select(-c(Notes, `Author (Year)`, Outcome, Measure)) %>% 
  rename(study_id = `STUDYID`) %>%
  drop_na(study_id) %>%
  select(study_id, type, msr, sort(current_vars())) %>% 
  remove_empty() %>% 
  pivot_wider(names_from = msr, values_from = c(-study_id, -type, -msr)) %>% 
  remove_empty()

df_hlm2 <-
  read_xlsx(data_file, sheet = "HLM Effects 2") %>% 
  mutate(
    type = str_sub(Outcome, 1, 3),
    msr = str_sub(Outcome, 4, 4),
  ) %>% 
  select(-c(Notes, `Author (Year)`, Outcome, Measure)) %>% 
  rename(study_id = `STUDYID`) %>%
  drop_na(study_id) %>%
  select(study_id, type, msr, sort(current_vars())) %>% 
  remove_empty() %>% 
  pivot_wider(names_from = msr, values_from = c(-study_id, -type, -msr)) %>% 
  remove_empty()


df_hlm3 <-
  read_xlsx(data_file, sheet = "HLM Effects 3") %>% 
  mutate(
    type = str_sub(Outcome, 1, 3),
    msr = str_sub(Outcome, 4, 4),
  ) %>% 
  select(-c(Notes, `Author (Year)`, Outcome, Measure)) %>% 
  rename(study_id = `STUDYID`) %>%
  drop_na(study_id) %>%
  select(study_id, type, msr, sort(current_vars())) %>% 
  remove_empty() %>% 
  pivot_wider(names_from = msr, values_from = c(-study_id, -type, -msr)) %>% 
  remove_empty()


df_hlm4 <-
  read_xlsx(data_file, sheet = "HLM Effects 4") %>% 
  mutate(
    type = str_sub(Outcome, 1, 3),
    msr = str_sub(Outcome, 4, 4),
  ) %>% 
  select(-c(Notes, `Author (Year)`, Outcome, Measure)) %>% 
  rename(study_id = `STUDYID`) %>%
  drop_na(study_id) %>%
  select(study_id, type, msr, sort(current_vars())) %>% 
  remove_empty() %>% 
  pivot_wider(names_from = msr, values_from = c(-study_id, -type, -msr)) %>% 
  remove_empty()


df_hlm5 <-
  read_xlsx(data_file, sheet = "HLM Effects 5") %>% 
  select(-c("Coefficient from HLM", "se", "Pooled student level sd", "effect size")) %>% 
  mutate(
    type = str_sub(Outcome, 1, 3),
    msr = str_sub(Outcome, 4, 4),
  ) %>% 
  select(-c(Notes, `Author (Year)`, Outcome, Measure)) %>% 
  rename(study_id = `STUDYID`) %>%
  drop_na(study_id) %>%
  select(study_id, type, msr, sort(current_vars())) %>% 
  remove_empty() %>% 
  pivot_wider(names_from = msr, values_from = c(-study_id, -type, -msr)) %>% 
  remove_empty()


df_hlm <- 
  bind_rows(df_hlm1, df_hlm2, df_hlm3, df_hlm4, df_hlm5) %>%
  mutate(type = str_c(type, "HLM", sep = "-")) %>%
  rename(
    C11MPost = C1MPost_1,
    C21MPost = C1MPost_2,
    C31MPost = C1MPost_3, 
    C41MPost = C1MPost_4, 
    C51MPost = C1MPost_5, 
    C61MPost = C1MPost_6, 
    C11MPre  = C1MPre_1,  
    C11NPost = C1NPost_1,
    C21NPost = C1NPost_2, 
    C31NPost = C1NPost_3, 
    C41NPost = C1NPost_4,
    C51NPost = C1NPost_5, 
    C61NPost = C1NPost_6, 
    C11NPre = C1NPre_1,  
    C11SPost = C1SPost_1, 
    C21SPost = C1SPost_2, 
    C31SPost = C1SPost_3, 
    C41SPost = C1SPost_4,
    C51SPost = C1SPost_5, 
    C61SPost = C1SPost_6, 
    C11SPre = C1SPre_1,  
    T11MPost = T1MPost_1, 
    T21MPost = T1MPost_2, 
    T31MPost = T1MPost_3, 
    T41MPost = T1MPost_4, 
    T51MPost = T1MPost_5, 
    T61MPost = T1MPost_6, 
    T11MPre = T1MPre_1, 
    T11NPost = T1NPost_1, 
    T21NPost = T1NPost_2, 
    T31NPost = T1NPost_3, 
    T41NPost = T1NPost_4, 
    T51NPost = T1NPost_5, 
    T61NPost = T1NPost_6, 
    T11NPre = T1NPre_1,  
    T11SPost = T1SPost_1, 
    T21SPost = T1SPost_2, 
    T31SPost = T1SPost_3,
    T41SPost = T1SPost_4, 
    T51SPost = T1SPost_5, 
    T61SPost = T1SPost_6, 
    T11SPre = T1SPre_1,  
    C21MPre = C1MPre_2, 
    C41MPre = C1MPre_4,  
    C21NPre = C1NPre_2,  
    C41NPre = C1NPre_4,  
    C21SPre = C1SPre_2,  
    C41SPre = C1SPre_4,
    T21MPre = T1MPre_2,  
    T41MPre = T1MPre_4,  
    T21NPre = T1NPre_2, 
    T41NPre = T1NPre_4,  
    T21SPre = T1SPre_2, 
    T41SPre = T1SPre_4, 
    C31MPre = C1MPre_3,  
    C31NPre = C1NPre_3,  
    C31SPre = C1SPre_3,  
    T31MPre = T1MPre_3,
    T31NPre = T1NPre_3,  
    T31SPre = T1SPre_3 
  ) %>% 
  remove_empty()

# remove redundant dfs
rm(df_hlm1, df_hlm2, df_hlm3, df_hlm4, df_hlm5)
rm(df_es1, df_es2, df_es3, df_es4, df_es5, df_es6)
```


```{r}
df_raw <- bind_rows(df_raw, df_hlm)

# remove redundant rows
df_raw$na_count <- apply(df_raw, 1, function(x) sum(is.na(x)))
#df_raw %>% filter(na_count >= (ncol(df_raw) - 3)) %>% remove_empty()
df_raw <- df_raw %>% filter(na_count < (ncol(df_raw) - 3))

#df_raw %>% arrange(-na_count) %>% count(na_count) %>% mutate(na_count = na_count/3)
#head(1) %>% remove_empty() %>% glimpse()
```


```{r, eval=FALSE}
# general checks
df_raw %>% get_dupes()
df_raw %>% count(type)
df_raw %>% summarize_at(vars(1, 2, 210), ~ mean(is.na(.)))
df_raw %>% get_dupes(type, study_id) %>% remove_empty()
```


### Study and measure overview

```{r}
# Add in correct author (year)
df_raw <-
  df_raw %>% 
  inner_join(
    read_xlsx(data_file, sheet = "All Studies") %>% 
      select(study_id = `STUDYID`, AUTYR = `Author (Year)`) %>% 
      drop_na(AUTYR),
    by = "study_id"
  ) %>% 
  relocate(type, study_id, AUTYR) %>% 
  arrange(type, study_id, AUTYR)

df_raw %>%
  mutate(
    type = if_else(type == "WCSN", "DSN", type),
    type = if_else(type == "WCRD", "DRD", type),
  ) %>% 
  distinct(AUTYR, type) %>% 
  arrange(AUTYR, type) %>% 
  group_by(AUTYR) %>% 
  mutate(n = row_number()) %>%
  ungroup() %>% 
  pivot_wider(names_from = n, values_from = type, names_prefix = "Measure ") %>% 
  rename(`Author (Year)` = AUTYR) %>% 
  datatable()
```

---

<br/>

### Calculating effect sizes


```{r}
### Post only

df_post <- df_raw

for (a in 1:9) {
  for (t in 1:9) {
    for (c in 1:9) {
      if (
        str_glue("T{t}{a}MPost") %in% colnames(df_post) & 
        str_glue("C{c}{a}MPost") %in% colnames(df_post)
      ) {
        df_post <-
          escalc(
            data = df_post,
            measure = "SMD",
            m1i = df_post[, str_c("T", t, a, "MPost")] %>% unlist(),
            m2i = df_post[, str_c("C", c, a, "MPost")] %>% unlist(),
            sd1i = df_post[, str_c("T", t, a, "SPost")] %>% unlist(),
            sd2i = df_post[, str_c("C", c, a, "SPost")] %>% unlist(),
            n1i = df_post[, str_c("T", t, a, "NPost")] %>% unlist(),
            n2i = df_post[, str_c("C", c, a, "NPost")] %>% unlist(),
            var.names = c(str_glue("ES{a}_{t}{c}"), str_glue("EV{a}_{t}{c}"))
          )
      }
    }
  }
}

df_post <-
  df_post %>% 
  select(study_id, AUTYR, type, starts_with("ES")) %>%
  pivot_longer(cols = starts_with("ES"), names_to = "num", values_to = "ES", values_drop_na = T) %>%
  mutate(num = str_sub(num, 3)) %>% 
  left_join(
    df_post %>% 
      select(study_id, AUTYR, type, starts_with("EV")) %>% 
      pivot_longer(cols = starts_with("EV"), names_to = "num", values_to = "EV", values_drop_na = T) %>% 
      mutate(num = str_sub(num, 3)),
    by = c("study_id", "AUTYR", "type", "num")
  )
```




```{r}
# Pre and Post

df_prepost <- df_raw

# treatment (post-pre)
for (a in 1:9) {
  for (t in 1:9) {
    if (str_glue("T{t}{a}MPost") %in% colnames(df_prepost) & str_glue("T{t}{a}MPre") %in% colnames(df_prepost)) {
      df_prepost <-
        escalc(
          data = df_prepost,
          measure = "SMCR",
          m1i = df_prepost[, str_c("T", t, a, "MPost")] %>% unlist(),
          m2i = df_prepost[, str_c("T", t, a, "MPre")] %>% unlist(),
          sd1i = df_prepost[, str_c("T", t, a, "SPre")] %>% unlist(),
          ni = df_prepost[, str_c("T", t, a, "NPost")] %>% unlist(),
          ri = rep(0.5, 183),
          var.names = c(str_glue("TES{a}_{t}"), str_glue("TEV{a}_{t}"))
        )
    }
  }
}

# control (post-pre)
for (a in 1:9) {
  for (c in 1:9) {
    if (str_glue("C{c}{a}MPost") %in% colnames(df_prepost) & str_glue("C{c}{a}MPre") %in% colnames(df_prepost)) {
      df_prepost <-
        escalc(
          data = df_prepost,
          measure = "SMCR",
          m1i = df_prepost[, str_c("C", c, a, "MPost")] %>% unlist(),
          m2i = df_prepost[, str_c("C", c, a, "MPre")] %>% unlist(),
          sd1i = df_prepost[, str_c("C", c, a, "SPre")] %>% unlist(),
          ni = df_prepost[, str_c("C", c, a, "NPost")] %>% unlist(),
          ri = rep(0.5, 183),
          var.names = c(str_glue("CES{a}_{c}"), str_glue("CEV{a}_{c}"))
        )
    }
  }
}



# ES and EV taken together
for (a in 1:9) {
  for (t in 1:9) {
    for (c in 1:9) {
      if (
        !(str_glue("TES{a}_{t}") %in% colnames(df_prepost)) | 
        !(str_glue("TEV{a}_{t}") %in% colnames(df_prepost)) |
        !(str_glue("CES{a}_{c}") %in% colnames(df_prepost)) | 
        !(str_glue("CEV{a}_{c}") %in% colnames(df_prepost))
      ) {
        next
      }
      # subtracting effect size
      df_prepost[, str_c("ES", a, "_", t, c)] <- 
        (df_prepost[, str_c("TES", a, "_", t)] %>% unlist()) -
        (df_prepost[, str_c("CES", a, "_", c)] %>% unlist())
      # adding variance
      df_prepost[, str_c("EV", a, "_", t, c)] <- 
        (df_prepost[, str_c("TEV", a, "_", t)] %>% unlist()) +
        (df_prepost[, str_c("CEV", a, "_", c)] %>% unlist())
    }
  }
}

df_prepost <-
  df_prepost %>% 
  select(study_id, AUTYR, type, starts_with("ES")) %>% 
  pivot_longer(cols = starts_with("ES"), names_to = "num", values_to = "ES", values_drop_na = T) %>%
  mutate(num = str_sub(num, 3)) %>% 
  left_join(
    df_prepost %>%
      select(study_id, AUTYR, type, starts_with("EV")) %>% 
      pivot_longer(cols = starts_with("EV"), names_to = "num", values_to = "EV", values_drop_na = T) %>% 
      mutate(num = str_sub(num, 3)),
    by = c("study_id", "AUTYR", "type", "num")
  )
```


```{r}
df_es_calc <-
  full_join(df_prepost, df_post, by = c("study_id", "AUTYR", "type", "num")) %>% 
  mutate(
    ES.x = if_else(is.na(ES.x) & !is.na(ES.y), ES.y, ES.x),
    EV.x = if_else(is.na(EV.x) & !is.na(EV.y), EV.y, EV.x)
  ) %>% 
  select(study_id, AUTYR, type, ES = ES.x, EV = EV.x)

# anti_join(df_post, df_prepost, by = c("study_id", "AUTYR", "type", "num")) %>% count(study_id)
```



```{r, fig.retina=4}
#### Combining all
df_append <- 
  bind_rows(df_es_calc, df_es_direct) %>% 
  mutate(
    type = if_else(type == "WCSN", "DSN", type),  # fixing WCSN --> DSN
    type = if_else(type == "WCRD", "DRD", type),  # fixing WCRD --> DRD
    type = str_replace(type, "-HLM", ""), # removing HLM as separate sub-type
  ) %>%
  arrange(type, study_id) %>%
  select(type, stdid = study_id, AUTYR, everything()) %>% 
  distinct()

cor_es <-
  df_append %>%
  unite("type_stdid", c("type", "stdid")) %>% 
  agg(id = type_stdid, es = ES, var = EV, method = "BHHR", data = .) %>% 
  separate(id, c("type", "stdid")) %>% 
  rename(ES = es, EV = var)

df_clean <-
  df_append %>% 
  distinct(type, stdid, AUTYR) %>%
  mutate(stdid = as.character(stdid)) %>% 
  left_join(cor_es, by = c("type", "stdid")) %>% 
  mutate_if(is.character, ~ str_replace_all(., '[\n\t]', '')) %>% 
  arrange(type, stdid)

rm(df_es_calc, df_es_direct, df_post, df_prepost, cor_es, df_raw, df_append, df_hlm, a, c, t)
```


```{r}
## add moderators ##

moderators <-
  read_xlsx(here::here("data/Revised Tables.xlsx")) %>%
  remove_empty() %>% 
  clean_names() %>% 
  transmute(
    stdid = as.character(studyid),
    outside_us = if_else(outside_us == "Yes", 1L, 0L),
    low_income_included = if_else(lowinc33 == "Yes", 1L, 0L),
    second_lang_included = if_else(seclang33 == "Yes", 1L, 0L),
    stu_disability_included = if_else(stdis33 == "Yes", 1L, 0L),
    grade = case_when(
      k == 1 ~ "K-2",
      gr1 == 1 ~ "K-2",
      gr2 == 1 ~ "K-2",
      gr3 == 1 ~ "3-5",
      gr4 == 1 ~ "3-5",
      gr5 == 1 ~ "3-5",
      TRUE ~ NA_character_
    ),
    pedagogy = case_when(
      pedagogy == 1 ~ "Behavioral",
      pedagogy == 2 ~ "Cognitive",
      pedagogy == 3 ~ "Constructivist",
      TRUE ~ NA_character_
    ),
    instructional_context = case_when(
      ins_cont_i0 == 0 ~ "Individual only",
      ins_cont_i0 == 1 ~ "Other than individual",
      TRUE ~ NA_character_
    ),
    tech_plus1,
    typetech,
    gamification = if_else(gamification == "Yes", 1L, 0L),
    adaptivity = if_else(adaptivity == "Yes", 1L, 0L),
    feedback = if_else(feedback == "Yes", 1L, 0L),
    teach_tr = if_else(teach_tr == "Yes", 1L, 0L),
    design,
    control,
    avghrs = case_when(
      avghrs >= 0 & avghrs <= 10 ~ "0-10",
      avghrs > 10 & avghrs <= 20 ~ "11-20",
      avghrs > 20 & avghrs <= 30 ~ "21-30",
      avghrs > 30 & avghrs <= 40 ~ "31-40",
      avghrs > 40 & avghrs <= 50 ~ "41-50",
      avghrs > 50 ~ "50+",
      TRUE ~ NA_character_
    )
  )


df_clean <-
  df_clean %>%
  left_join(moderators, by = "stdid") %>%
  relocate(type, stdid, AUTYR) %>%
  arrange(type, stdid, AUTYR)

rm(moderators)
```



```{r}
#### Filtered datasets
df_c <- df_clean %>% filter(type %in% c("CRD", "CRP", "CSN"))
df_d <- df_clean %>% filter(type %in% c("DRD", "DRP", "DSN"))
df_l <- df_clean %>% filter(type %in% c("LRD", "LRP", "LSN"))
df_w <- df_clean %>% filter(type %in% c("WPRD", "WPSN"))
```



```{r}
# displaying clean df

df_clean %>%
  relocate(AUTYR, stdid) %>%
  arrange(AUTYR, type) %>% 
  select(`Author (Year)` = AUTYR, type, ES, EV) %>% 
  mutate_if(is.numeric, ~ round(., 4)) %>% 
  datatable()
```


---

<br/>

### Synthesizing effect sizes

#### Decoding

```{r}
model_d <-
  df_d %>%
  mutate(type = factor(type, levels = c("DRP", "DRD", "DSN"))) %>% 
  mutate(
    AUTYR = if_else(str_detect(type, "D$"), str_c(AUTYR, " "), AUTYR),
    AUTYR = if_else(str_detect(type, "N$"), str_c(AUTYR, "  "), AUTYR),
  ) %>%
  arrange(desc(type), desc(ES)) %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = AUTYR
  )

model_dr <-
  df_d %>%
  filter(str_detect(type, "^DR")) %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = stdid
  )

model_drp <-
  df_d %>%
  filter(type == "DRP") %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = stdid
  )

model_drd <-
  df_d %>%
  filter(type == "DRD") %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = stdid
  )

model_dsn <-
  df_d %>%
  filter(type == "DSN") %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = stdid
  )

# df_d %>% mutate(type = factor(type, levels = c("DRP", "DRD", "DSN"))) %>% count(type)
# df_d %>% arrange(type, ES)
```

Overall:

```{r}
model_d
```


Researcher-Developed proximal:

```{r}
model_drp
```

Researcher-Developed distal:

```{r}
model_drd
```

Researcher-Developed (all):

```{r}
model_dr
```

Standardized:

```{r}
model_dsn
```


```{r, fig.retina = 4, fig.asp=3}
a1 <- 4
a2 <- 4 + nrow(df_d %>% filter(type == "DSN")) - 1

b1 <- a2 + 6
b2 <- b1 + nrow(df_d %>% filter(type == "DRD")) - 1

c1 <- b2 + 6
c2 <- c1 + nrow(df_d %>% filter(type == "DRP")) - 1

forest(
  model_d,
  xlab = "Decoding Related Skills",
  addcred = T, 
  header = T,
  xlim = c(-6, 6),
  ylim = c(0, c2 + 6),
  rows = c(a1:a2, b1:b2, c1:c2),
  pch = 21,
  bg = "grey",
  lwd = 1.5
)

op <- par(cex = 1.25, font = 4)

text(-6, c(a2 + 2, b2 + 2, c2 + 2), pos = 4, c("Standardized", "Researcher-Developed (Distal)", "Researcher-Developed (Proximal)"))

addpoly(model_drp, row = b2 + 4, cex = 1.25, col = "white", lwd = 3)
addpoly(model_drd, row = a2 + 4, cex = 1.25, col = "white", lwd = 3)
addpoly(model_dsn, row = 2, cex = 1.25, col = "white", lwd = 3)
```

---

<br/>

#### Reading Comprehension

```{r}
model_c <-
  df_c %>%
  mutate(type = factor(type, levels = c("CRP", "CRD", "CSN"))) %>% 
  mutate(
    AUTYR = if_else(str_detect(type, "N$"), str_c(AUTYR, " "), AUTYR),
  ) %>%
  arrange(desc(type), desc(ES)) %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = AUTYR
  )


model_cr <-
  df_c %>%
  filter(str_detect(type, "^CR")) %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = stdid
  )

model_csn <-
  df_c %>%
  filter(type == "CSN") %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = stdid
  )
```


Overall:

```{r}
model_c
```


Researcher-Developed (Distal):

```{r}
model_cr
```

Standardized:

```{r}
model_csn
```



```{r, fig.retina = 4, fig.asp=3}
a1 <- 4
a2 <- 4 + nrow(df_c %>% filter(type == "CSN")) - 1

b1 <- a2 + 6
b2 <- b1 + nrow(df_c %>% filter(type == "CRD")) - 1

forest(
  model_c,
  xlab = "Reading Comprehension Skills",
  addcred = T, 
  header = T,
  xlim = c(-6, 5),
  ylim = c(0, b2 + 6),
  rows = c(a1:a2, b1:b2),
  pch = 21,
  bg = "grey",
  lwd = 1.5
)

op <- par(cex = 1.25, font = 4)

text(-6, c(a2 + 2, b2 + 2), pos = 4, c("Standardized", "Researcher-Developed (Distal)"))

addpoly(model_cr, row = a2 + 4, cex = 1.25, col = "white", lwd = 3)
addpoly(model_csn, row = 2, cex = 1.25, col = "white", lwd = 3)
```



---

<br/>


#### Language Comprehension

```{r}
model_l <-
  df_l %>%
  mutate(type = factor(type, levels = c("LRP", "LRD", "LSN"))) %>%
  mutate(
    AUTYR = if_else(str_detect(type, "D$"), str_c(AUTYR, " "), AUTYR),
    AUTYR = if_else(str_detect(type, "N$"), str_c(AUTYR, "  "), AUTYR),
  ) %>% 
  arrange(desc(type), desc(ES)) %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = AUTYR
  )

model_lr <-
  df_l %>%
  filter(str_detect(type, "^LR")) %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = stdid
  )

model_lrd <-
  df_l %>%
  filter(type == "LRD") %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = stdid
  )

model_lrp <-
  df_l %>%
  filter(type == "LRP") %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = stdid
  )

model_lsn <-
  df_l %>%
  filter(type == "LSN") %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = stdid
  )

# df_l %>% arrange(type, ES)
# df_l %>% mutate(type = factor(type, levels = c("LRP", "LRD", "LSN"))) %>% count(type)
```


Overall:

```{r}
model_l
```


Researcher-Developed proximal:

```{r}
model_lrp
```

Researcher-Developed distal:

```{r}
model_lrd
```

Researcher-Developed (all):

```{r}
model_lr
```

Standardized:

```{r}
model_lsn
```




```{r, fig.retina = 4, fig.asp=3}
a1 <- 4
a2 <- 4 + nrow(df_l %>% filter(type == "LSN")) - 1

b1 <- a2 + 6
b2 <- b1 + nrow(df_l %>% filter(type == "LRD")) - 1

c1 <- b2 + 6
c2 <- c1 + nrow(df_l %>% filter(type == "LRP")) - 1

forest(
  model_l,
  xlab = "Language Comprehension Related Skills",
  addcred = T, 
  header = T,
  xlim = c(-7, 7),
  ylim = c(0, c2 + 6),
  rows = c(a1:a2, b1:b2, c1:c2),
  pch = 21,
  bg = "grey",
  lwd = 1.5
)

op <- par(cex = 1.25, font = 4)

text(-7, c(a2 + 2, b2 + 2, c2 + 2), pos = 4, c("Standardized", "Researcher-Developed (Distal)", "Researcher-Developed (Proximal)"))

addpoly(model_lrp, row = b2 + 4, cex = 1.25, col = "white", lwd = 3)
addpoly(model_lrd, row = a2 + 4, cex = 1.25, col = "white", lwd = 3)
addpoly(model_lsn, row = 2, cex = 1.25, col = "white", lwd = 3)
```



---

<br/>

#### Writing Proficiency

```{r}
model_w <-
  df_w %>%
  arrange(desc(type), desc(ES)) %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = AUTYR
  )

model_wprd <-
  df_w %>%
  filter(type == "WPRD") %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = stdid
  )

model_wpsn <-
  df_w %>%
  filter(type == "WPSN") %>% 
  rma(
    yi = ES, 
    vi = EV, 
    data = ., 
    method = "REML",
    slab = stdid
  )

# df_w %>% arrange(type, ES)
```



Overall:

```{r}
model_w
```


Researcher-Developed distal:

```{r}
model_wprd
```


Standardized:

```{r}
model_wpsn
```



```{r, fig.retina = 4, fig.asp = 1}
a1 <- 4
a2 <- 4 + nrow(df_w %>% filter(type == "WPSN")) - 1

b1 <- a2 + 6
b2 <- b1 + nrow(df_w %>% filter(type == "WPRD")) - 1

forest(
  model_w,
  xlab = "Writing Skills",
  addcred = T, 
  header = T,
  xlim = c(-4, 5),
  ylim = c(-2, b2 + 6),
  rows = c(a1:a2, b1:b2),
  pch = 21,
  bg = "grey",
  lwd = 1.5
)

op <- par(cex = 1.25, font = 4)

text(-4, c(a2 + 2, b2 + 2), pos = 4, c("Standardized", "Researcher-Developed (Distal)"))

addpoly(model_wprd, row = a2 + 4, cex = 1.25, col = "white", lwd = 3)
addpoly(model_wpsn, row = 2, cex = 1.25, col = "white", lwd = 3)
```


---

<!-- <br/> -->

<!-- ### Moderator analyses -->

<!-- #### Decoding -->

<!-- ```{r, results='asis'} -->
<!-- lm1 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ design) -->
<!-- lm2 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ grade) -->
<!-- lm3 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ t1_number_of_hours) -->
<!-- lm4 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ location) -->
<!-- lm5 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ t1_group_size_more_than_1) -->
<!-- lm6 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ t1_tech_techplus) -->
<!-- lm7 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ t1_tech_type) -->
<!-- lm8 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ t1_instructional_focus) -->
<!-- lm9 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ dissertation) -->
<!-- lm9.5 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ teacher_training) -->

<!-- knitreg(list(lm1, lm2, lm3, lm4, lm5, lm6, lm7, lm8, lm9, lm9.5), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Design", "Grade", "Hours", "Location", "Group size", "Tech", "Tech type", "Instructional focus", "Dissertation", "Teacher Training")) -->
<!-- ``` -->


<!-- Additional moderators: -->

<!-- ```{r, results='asis'} -->
<!-- lm10 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ disabilities_inc) -->
<!-- lm11 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ low_ses) -->
<!-- lm12 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ l2inc) -->
<!-- lm13 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ adaptive) -->
<!-- lm14 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ gamification) -->
<!-- lm15 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ personalization_inc) -->
<!-- lm16 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ integrated) -->
<!-- lm17 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ factor(stance)) -->
<!-- lm18 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ l2targeted) -->

<!-- knitreg(list(lm10, lm11, lm12, lm13, lm14, lm15, lm16, lm17, lm18), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Disabilities incl", "Low SES incl", "L2 incl", "Adaptive", "Gamification", "Personalized", "Integrated", "Stance", "L2 targeted")) -->
<!-- ``` -->



<!-- Group size [1 v (2 and 3)]: -->

<!-- Group size 2 or 3 has larger effects than group size 1, but not statistically significant. -->

<!-- ```{r, results='asis'} -->
<!-- df_d %>% -->
<!--   filter(group_size %in% c(1, 2, 3)) %>% -->
<!--   mutate(group_size = if_else(group_size == 1, "1", "2-3")) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ group_size) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Group size [1 v 4]: -->

<!-- No group size 4 for decoding studies. -->

<!-- ```{r, results='asis', eval=F} -->
<!-- df_d %>% -->
<!--   filter(group_size %in% c(1, 4)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size)) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Group size [1 v 5]: -->

<!-- Group size 5 has larger effects than 1, but not significant. -->

<!-- ```{r, results='asis'} -->
<!-- df_d %>% -->
<!--   filter(group_size %in% c(1, 5)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size)) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Instructional focus [2 (comprehension) vs 4 (combo)]: -->

<!-- Comprehension effect sizes are lower than combo effect sizes. The difference is not statistically significant though. -->

<!-- ```{r, results='asis'} -->
<!-- df_d %>% -->
<!--   filter(t1_instructional_focus %in% c("Comprehension", "Combo")) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ t1_instructional_focus) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Instructional focus")) -->
<!-- ``` -->


<!-- Pedagogical stance [1 vs 2]: -->

<!-- Stance 2 effect sizes are lower than Stance 1 effect sizes. The difference is not statistically significant though. -->

<!-- ```{r, results='asis'} -->
<!-- df_d %>% -->
<!--   filter(stance > 0) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(stance)) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance")) -->
<!-- ``` -->


<!-- Pedagogical stance [0 vs 1/2]: -->

<!-- ```{r, results='asis'} -->
<!-- df_d %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ stance_0_vs_12) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance (0 vs 1/2)")) -->
<!-- ``` -->


<!-- Hours [more than 20]: -->

<!-- ```{r, results='asis'} -->
<!-- df_d %>% -->
<!--   mutate(hours_more_than_20 = if_else(t1_number_of_hours > 20, 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ hours_more_than_20) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Hours (more than 20)")) -->
<!-- ``` -->


<!-- --- -->


<!-- #### Reading Comprehension -->

<!-- ```{r, results='asis'} -->
<!-- lm1 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ design) -->
<!-- lm2 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ grade) -->
<!-- lm3 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ t1_number_of_hours) -->
<!-- lm4 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ location) -->
<!-- lm5 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ t1_group_size_more_than_1) -->
<!-- lm6 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ t1_tech_techplus) -->
<!-- lm7 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ t1_tech_type) -->
<!-- lm8 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ t1_instructional_focus) -->
<!-- lm9 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ dissertation) -->
<!-- lm9.5 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ teacher_training) -->

<!-- knitreg(list(lm1, lm2, lm3, lm4, lm5, lm6, lm7, lm8, lm9, lm9.5), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Design", "Grade", "Hours", "Location", "Group size", "Tech", "Tech type", "Instructional focus", "Dissertation", "Teacher training")) -->
<!-- ``` -->

<!-- Additional moderators: -->

<!-- ```{r, results='asis'} -->
<!-- lm10 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ disabilities_inc) -->
<!-- lm11 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ low_ses) -->
<!-- lm12 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ l2inc) -->
<!-- lm13 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ adaptive) -->
<!-- lm14 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ gamification) -->
<!-- lm15 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ personalization_inc) -->
<!-- lm16 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ integrated) -->
<!-- lm17 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ factor(stance)) -->
<!-- lm18 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ l2targeted) -->

<!-- knitreg(list(lm10, lm11, lm12, lm13, lm14, lm15, lm16, lm17, lm18), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Disabilities incl", "Low SES incl", "L2 incl", "Adaptive", "Gamification", "Personalized", "Integrated", "Stance", "L2 targeted")) -->
<!-- ``` -->



<!-- Group size [1 v (2 and 3)]: -->


<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   filter(group_size %in% c(1, 2, 3)) %>% -->
<!--   mutate(group_size = if_else(group_size == 1, "1", "2-3")) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ group_size) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Group size [1 v 4]: -->

<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   filter(group_size %in% c(1, 4)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size)) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Group size [1 v 5]: -->


<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   filter(group_size %in% c(1, 5)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size)) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Instructional focus [2 (comprehension) vs 4 (combo)]: -->


<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   filter(t1_instructional_focus %in% c("Comprehension", "Combo")) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ t1_instructional_focus) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Instructional focus")) -->
<!-- ``` -->


<!-- Pedagogical stance [1 vs 2]: -->


<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   filter(stance > 0) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(stance)) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance")) -->
<!-- ``` -->


<!-- Pedagogical stance [0 vs 1/2]: -->

<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ stance_0_vs_12) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance (0 vs 1/2)")) -->
<!-- ``` -->


<!-- Hours [more than 20]: -->

<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   mutate(hours_more_than_20 = if_else(t1_number_of_hours > 20, 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ hours_more_than_20) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Hours (more than 20)")) -->
<!-- ``` -->


<!-- --- -->


<!-- #### Language Comprehension -->

<!-- ```{r, results='asis'} -->
<!-- lm1 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ design) -->
<!-- lm2 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ grade) -->
<!-- lm3 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ t1_number_of_hours) -->
<!-- lm4 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ location) -->
<!-- lm5 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ t1_group_size_more_than_1) -->
<!-- lm6 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ t1_tech_techplus) -->
<!-- lm7 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ t1_tech_type) -->
<!-- lm8 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ t1_instructional_focus) -->
<!-- lm9 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ dissertation) -->
<!-- lm9.5 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ teacher_training) -->

<!-- knitreg(list(lm1, lm2, lm3, lm4, lm5, lm6, lm7, lm8, lm9, lm9.5), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Design", "Grade", "Hours", "Location", "Group size", "Tech", "Tech type", "Instructional focus", "Dissertation", "Teacher training")) -->
<!-- ``` -->

<!-- Additional moderators: -->

<!-- ```{r, results='asis'} -->
<!-- lm10 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ disabilities_inc) -->
<!-- lm11 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ low_ses) -->
<!-- lm12 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ l2inc) -->
<!-- lm13 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ adaptive) -->
<!-- lm14 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ gamification) -->
<!-- lm15 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ personalization_inc) -->
<!-- lm16 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ integrated) -->
<!-- lm17 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ factor(stance)) -->
<!-- lm18 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ l2targeted) -->

<!-- knitreg(list(lm10, lm11, lm12, lm13, lm14, lm15, lm16, lm17, lm18), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Disabilities incl", "Low SES incl", "L2 incl", "Adaptive", "Gamification", "Personalized", "Integrated", "Stance", "L2 targeted")) -->
<!-- ``` -->



<!-- Group size [1 v (2 and 3)]: -->

<!-- No variation exists for this variable. -->

<!-- ```{r, results='asis', eval = F} -->
<!-- df_l %>% -->
<!--   filter(group_size %in% c(1, 2, 3)) %>% -->
<!--   mutate(group_size = if_else(group_size == 1, "1", "2-3")) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ group_size) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Group size [1 v 4]: -->

<!-- No variation exists for this variable. -->

<!-- ```{r, results='asis', eval = F} -->
<!-- df_l %>% -->
<!--   filter(group_size %in% c(1, 4)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size)) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Group size [1 v 5]: -->


<!-- ```{r, results='asis'} -->
<!-- df_l %>% -->
<!--   filter(group_size %in% c(1, 5)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size)) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Instructional focus [2 (comprehension) vs 4 (combo)]: -->


<!-- ```{r, results='asis'} -->
<!-- df_l %>% -->
<!--   filter(t1_instructional_focus %in% c("Comprehension", "Combo")) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ t1_instructional_focus) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Instructional focus")) -->
<!-- ``` -->


<!-- Pedagogical stance [1 vs 2]: -->


<!-- ```{r, results='asis'} -->
<!-- df_l %>% -->
<!--   filter(stance > 0) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(stance)) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance")) -->
<!-- ``` -->


<!-- Pedagogical stance [0 vs 1/2]: -->

<!-- ```{r, results='asis'} -->
<!-- df_l %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ stance_0_vs_12) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance (0 vs 1/2)")) -->
<!-- ``` -->


<!-- Hours [more than 20]: -->

<!-- ```{r, results='asis'} -->
<!-- df_l %>% -->
<!--   mutate(hours_more_than_20 = if_else(t1_number_of_hours > 20, 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ hours_more_than_20) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Hours (more than 20)")) -->
<!-- ``` -->



<!-- --- -->

<!-- #### Writing Proficiency -->

<!-- ```{r, results='asis'} -->
<!-- lm1 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ design) -->
<!-- lm2 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ grade) -->
<!-- lm3 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ t1_number_of_hours) -->
<!-- lm4 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ location) -->
<!-- lm5 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ t1_group_size_more_than_1) -->
<!-- lm6 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ t1_tech_techplus) -->
<!-- lm7 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ t1_tech_type) -->
<!-- lm8 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ t1_instructional_focus) -->
<!-- lm9 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ dissertation) -->
<!-- lm9.5 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ teacher_training) -->

<!-- knitreg(list(lm1, lm2, lm3, lm4, lm5, lm6, lm7, lm8, lm9, lm9.5), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Design", "Grade", "Hours", "Location", "Group size", "Tech", "Tech type", "Instructional focus", "Dissertation", "Teacher training")) -->
<!-- ``` -->


<!-- Additional moderators: -->

<!-- ```{r, results='asis'} -->
<!-- lm10 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ disabilities_inc) -->
<!-- lm11 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ low_ses) -->
<!-- lm12 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ l2inc) -->
<!-- lm13 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ adaptive) -->
<!-- lm14 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ gamification) -->
<!-- lm15 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ personalization_inc) -->
<!-- lm16 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ integrated) -->
<!-- lm17 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ factor(stance)) -->
<!-- lm18 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ l2targeted) -->

<!-- knitreg(list(lm10, lm11, lm12, lm13, lm14, lm15, lm16, lm17, lm18), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Disabilities incl", "Low SES incl", "L2 incl", "Adaptive", "Gamification", "Personalized", "Integrated", "Stance", "L2 targeted")) -->
<!-- ``` -->




<!-- Group size [1 v (2 and 3)]: -->


<!-- No variation exists for this variable. -->

<!-- ```{r, results='asis', eval = F} -->
<!-- df_w %>% -->
<!--   filter(group_size %in% c(1, 2, 3)) %>% -->
<!--   mutate(group_size = if_else(group_size == 1, "1", "2-3")) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ group_size) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Group size [1 v 4]: -->

<!-- No variation exists for this variable. -->

<!-- ```{r, results='asis', eval = F} -->
<!-- df_w %>% -->
<!--   filter(group_size %in% c(1, 4)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size)) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Group size [1 v 5]: -->


<!-- ```{r, results='asis'} -->
<!-- df_w %>% -->
<!--   filter(group_size %in% c(1, 5)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size)) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Instructional focus [2 (comprehension) vs 4 (combo)]: -->


<!-- ```{r, results='asis'} -->
<!-- df_w %>% -->
<!--   filter(t1_instructional_focus %in% c("Comprehension", "Combo")) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ t1_instructional_focus) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Instructional focus")) -->
<!-- ``` -->


<!-- Pedagogical stance [1 vs 2]: -->


<!-- ```{r, results='asis'} -->
<!-- df_w %>% -->
<!--   filter(stance > 0) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(stance)) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance")) -->
<!-- ``` -->


<!-- Pedagogical stance [0 vs 1/2]: -->

<!-- ```{r, results='asis'} -->
<!-- df_w %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ stance_0_vs_12) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance (0 vs 1/2)")) -->
<!-- ``` -->


<!-- Hours [more than 20]: -->

<!-- ```{r, results='asis'} -->
<!-- df_w %>% -->
<!--   mutate(hours_more_than_20 = if_else(t1_number_of_hours > 20, 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ hours_more_than_20) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Hours (more than 20)")) -->
<!-- ``` -->


<!-- --- -->


<!-- ### Moderator analyses [Control for Type] -->

<!-- #### Decoding -->

<!-- ```{r, results='asis'} -->
<!-- lm1 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ design + type) -->
<!-- lm2 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ grade + type) -->
<!-- lm3 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ t1_number_of_hours + type) -->
<!-- lm4 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ location + type) -->
<!-- lm5 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ t1_group_size_more_than_1 + type) -->
<!-- lm6 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ t1_tech_techplus + type) -->
<!-- lm7 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ t1_tech_type + type) -->
<!-- lm8 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ t1_instructional_focus + type) -->
<!-- lm9 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ dissertation + type) -->
<!-- lm9.5 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ teacher_training + type) -->

<!-- knitreg(list(lm1, lm2, lm3, lm4, lm5, lm6, lm7, lm8, lm9, lm9.5), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Design", "Grade", "Hours", "Location", "Group size", "Tech", "Tech type", "Instructional focus", "Dissertation", "Teacher Training")) -->
<!-- ``` -->


<!-- Additional moderators: -->

<!-- ```{r, results='asis'} -->
<!-- lm10 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ disabilities_inc + type) -->
<!-- lm11 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ low_ses + type) -->
<!-- lm12 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ l2inc + type) -->
<!-- lm13 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ adaptive + type) -->
<!-- lm14 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ gamification + type) -->
<!-- lm15 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ personalization_inc + type) -->
<!-- lm16 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ integrated + type) -->
<!-- lm17 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ factor(stance) + type) -->
<!-- lm18 <- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ l2targeted + type) -->

<!-- knitreg(list(lm10, lm11, lm12, lm13, lm14, lm15, lm16, lm17, lm18), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Disabilities incl", "Low SES incl", "L2 incl", "Adaptive", "Gamification", "Personalized", "Integrated", "Stance", "L2 targeted")) -->
<!-- ``` -->



<!-- Group size [1 v (2 and 3)]: -->

<!-- Group size 2 or 3 has larger effects than group size 1, but not statistically significant. -->

<!-- ```{r, results='asis'} -->
<!-- df_d %>% -->
<!--   filter(group_size %in% c(1, 2, 3)) %>% -->
<!--   mutate(group_size = if_else(group_size == 1, "1", "2-3")) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ group_size + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Group size [1 v 4]: -->

<!-- No group size 4 for decoding studies. -->



<!-- Group size [1 v 5]: -->


<!-- ```{r, results='asis'} -->
<!-- df_d %>% -->
<!--   filter(group_size %in% c(1, 5)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size) + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Instructional focus [2 (comprehension) vs 4 (combo)]: -->


<!-- ```{r, results='asis'} -->
<!-- df_d %>% -->
<!--   filter(t1_instructional_focus %in% c("Comprehension", "Combo")) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ t1_instructional_focus + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Instructional focus")) -->
<!-- ``` -->


<!-- Pedagogical stance [1 vs 2]: -->

<!-- Stance 2 effect sizes are lower than Stance 1 effect sizes. The difference is not statistically significant though. -->

<!-- ```{r, results='asis'} -->
<!-- df_d %>% -->
<!--   filter(stance > 0) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(stance) + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance")) -->
<!-- ``` -->


<!-- Pedagogical stance [0 vs 1/2]: -->

<!-- ```{r, results='asis'} -->
<!-- df_d %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ stance_0_vs_12 + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance (0 vs 1/2)")) -->
<!-- ``` -->


<!-- Hours [more than 20]: -->

<!-- ```{r, results='asis'} -->
<!-- df_d %>% -->
<!--   mutate(hours_more_than_20 = if_else(t1_number_of_hours > 20, 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ hours_more_than_20 + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Hours (more than 20)")) -->
<!-- ``` -->


<!-- --- -->


<!-- #### Reading Comprehension -->

<!-- ```{r, results='asis'} -->
<!-- lm1 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ design + type) -->
<!-- lm2 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ grade + type) -->
<!-- lm3 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ t1_number_of_hours + type) -->
<!-- lm4 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ location + type) -->
<!-- lm5 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ t1_group_size_more_than_1 + type) -->
<!-- lm6 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ t1_tech_techplus + type) -->
<!-- lm7 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ t1_tech_type + type) -->
<!-- lm8 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ t1_instructional_focus + type) -->
<!-- lm9 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ dissertation + type) -->
<!-- lm9.5 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ teacher_training + type) -->

<!-- knitreg(list(lm1, lm2, lm3, lm4, lm5, lm6, lm7, lm8, lm9, lm9.5), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Design", "Grade", "Hours", "Location", "Group size", "Tech", "Tech type", "Instructional focus", "Dissertation", "Teacher training")) -->
<!-- ``` -->

<!-- Additional moderators: -->

<!-- ```{r, results='asis'} -->
<!-- lm10 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ disabilities_inc + type) -->
<!-- lm11 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ low_ses + type) -->
<!-- lm12 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ l2inc + type) -->
<!-- lm13 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ adaptive + type) -->
<!-- lm14 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ gamification + type) -->
<!-- lm15 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ personalization_inc + type) -->
<!-- lm16 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ integrated + type) -->
<!-- lm17 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ factor(stance) + type) -->
<!-- lm18 <- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ l2targeted + type) -->

<!-- knitreg(list(lm10, lm11, lm12, lm13, lm14, lm15, lm16, lm17, lm18), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Disabilities incl", "Low SES incl", "L2 incl", "Adaptive", "Gamification", "Personalized", "Integrated", "Stance", "L2 targeted")) -->
<!-- ``` -->



<!-- Group size [1 v (2 and 3)]: -->


<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   filter(group_size %in% c(1, 2, 3)) %>% -->
<!--   mutate(group_size = if_else(group_size == 1, "1", "2-3")) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ group_size + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Group size [1 v 4]: -->

<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   filter(group_size %in% c(1, 4)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size) + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Group size [1 v 5]: -->


<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   filter(group_size %in% c(1, 5)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size) + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Instructional focus [2 (comprehension) vs 4 (combo)]: -->


<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   filter(t1_instructional_focus %in% c("Comprehension", "Combo")) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ t1_instructional_focus + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Instructional focus")) -->
<!-- ``` -->


<!-- Pedagogical stance [1 vs 2]: -->


<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   filter(stance > 0) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(stance) + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance")) -->
<!-- ``` -->


<!-- Pedagogical stance [0 vs 1/2]: -->

<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ stance_0_vs_12 + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance (0 vs 1/2)")) -->
<!-- ``` -->


<!-- Hours [more than 20]: -->

<!-- ```{r, results='asis'} -->
<!-- df_c %>% -->
<!--   mutate(hours_more_than_20 = if_else(t1_number_of_hours > 20, 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ hours_more_than_20 + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Hours (more than 20)")) -->
<!-- ``` -->


<!-- --- -->


<!-- #### Language Comprehension -->

<!-- ```{r, results='asis'} -->
<!-- lm1 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ design + type) -->
<!-- lm2 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ grade + type) -->
<!-- lm3 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ t1_number_of_hours + type) -->
<!-- lm4 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ location + type) -->
<!-- lm5 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ t1_group_size_more_than_1 + type) -->
<!-- lm6 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ t1_tech_techplus + type) -->
<!-- lm7 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ t1_tech_type + type) -->
<!-- lm8 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ t1_instructional_focus + type) -->
<!-- lm9 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ dissertation + type) -->
<!-- lm9.5 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ teacher_training + type) -->

<!-- knitreg(list(lm1, lm2, lm3, lm4, lm5, lm6, lm7, lm8, lm9, lm9.5), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Design", "Grade", "Hours", "Location", "Group size", "Tech", "Tech type", "Instructional focus", "Dissertation", "Teacher training")) -->
<!-- ``` -->

<!-- Additional moderators: -->

<!-- ```{r, results='asis'} -->
<!-- lm10 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ disabilities_inc + type) -->
<!-- lm11 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ low_ses + type) -->
<!-- lm12 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ l2inc + type) -->
<!-- lm13 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ adaptive + type) -->
<!-- lm14 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ gamification + type) -->
<!-- lm15 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ personalization_inc + type) -->
<!-- lm16 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ integrated + type) -->
<!-- lm17 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ factor(stance) + type) -->
<!-- lm18 <- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ l2targeted + type) -->

<!-- knitreg(list(lm10, lm11, lm12, lm13, lm14, lm15, lm16, lm17, lm18), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Disabilities incl", "Low SES incl", "L2 incl", "Adaptive", "Gamification", "Personalized", "Integrated", "Stance", "L2 targeted")) -->
<!-- ``` -->



<!-- Group size [1 v (2 and 3)]: -->

<!-- No variation exists for this variable. -->


<!-- Group size [1 v 4]: -->

<!-- No variation exists for this variable. -->


<!-- Group size [1 v 5]: -->


<!-- ```{r, results='asis'} -->
<!-- df_l %>% -->
<!--   filter(group_size %in% c(1, 5)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size) + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Instructional focus [2 (comprehension) vs 4 (combo)]: -->


<!-- ```{r, results='asis'} -->
<!-- df_l %>% -->
<!--   filter(t1_instructional_focus %in% c("Comprehension", "Combo")) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ t1_instructional_focus + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Instructional focus")) -->
<!-- ``` -->


<!-- Pedagogical stance [1 vs 2]: -->


<!-- ```{r, results='asis'} -->
<!-- df_l %>% -->
<!--   filter(stance > 0) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(stance) + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance")) -->
<!-- ``` -->


<!-- Pedagogical stance [0 vs 1/2]: -->

<!-- ```{r, results='asis'} -->
<!-- df_l %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ stance_0_vs_12 + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance (0 vs 1/2)")) -->
<!-- ``` -->


<!-- Hours [more than 20]: -->

<!-- ```{r, results='asis'} -->
<!-- df_l %>% -->
<!--   mutate(hours_more_than_20 = if_else(t1_number_of_hours > 20, 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ hours_more_than_20 + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Hours (more than 20)")) -->
<!-- ``` -->



<!-- --- -->

<!-- #### Writing Proficiency -->

<!-- ```{r, results='asis'} -->
<!-- lm1 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ design + type) -->
<!-- lm2 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ grade + type) -->
<!-- lm3 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ t1_number_of_hours + type) -->
<!-- lm4 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ location + type) -->
<!-- lm5 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ t1_group_size_more_than_1 + type) -->
<!-- lm6 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ t1_tech_techplus + type) -->
<!-- lm7 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ t1_tech_type + type) -->
<!-- lm8 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ t1_instructional_focus + type) -->
<!-- lm9 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ dissertation + type) -->
<!-- lm9.5 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ teacher_training + type) -->

<!-- knitreg(list(lm1, lm2, lm3, lm4, lm5, lm6, lm7, lm8, lm9, lm9.5), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Design", "Grade", "Hours", "Location", "Group size", "Tech", "Tech type", "Instructional focus", "Dissertation", "Teacher training")) -->
<!-- ``` -->


<!-- Additional moderators: -->

<!-- ```{r, results='asis'} -->
<!-- lm10 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ disabilities_inc + type) -->
<!-- lm11 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ low_ses + type) -->
<!-- lm12 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ l2inc + type) -->
<!-- lm13 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ adaptive + type) -->
<!-- lm14 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ gamification + type) -->
<!-- lm15 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ personalization_inc + type) -->
<!-- lm16 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ integrated + type) -->
<!-- lm17 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ factor(stance) + type) -->
<!-- lm18 <- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ l2targeted + type) -->

<!-- knitreg(list(lm10, lm11, lm12, lm13, lm14, lm15, lm16, lm17, lm18), stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Disabilities incl", "Low SES incl", "L2 incl", "Adaptive", "Gamification", "Personalized", "Integrated", "Stance", "L2 targeted")) -->
<!-- ``` -->




<!-- Group size [1 v (2 and 3)]: -->


<!-- No variation exists for this variable. -->


<!-- Group size [1 v 4]: -->

<!-- No variation exists for this variable. -->


<!-- Group size [1 v 5]: -->


<!-- ```{r, results='asis'} -->
<!-- df_w %>% -->
<!--   filter(group_size %in% c(1, 5)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(group_size) + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Group size")) -->
<!-- ``` -->


<!-- Instructional focus [2 (comprehension) vs 4 (combo)]: Not enough variation in data controlling for type. -->

<!-- Pedagogical stance [1 vs 2]: -->


<!-- ```{r, results='asis'} -->
<!-- df_w %>% -->
<!--   filter(stance > 0) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ factor(stance) + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance")) -->
<!-- ``` -->


<!-- Pedagogical stance [0 vs 1/2]: -->

<!-- ```{r, results='asis'} -->
<!-- df_w %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ stance_0_vs_12 + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Pedagogical stance (0 vs 1/2)")) -->
<!-- ``` -->


<!-- Hours [more than 20]: -->

<!-- ```{r, results='asis'} -->
<!-- df_w %>% -->
<!--   mutate(hours_more_than_20 = if_else(t1_number_of_hours > 20, 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ hours_more_than_20 + type) %>%  -->
<!--   knitreg(include.ci = F, stars = c(0.01, 0.05, 0.1), include.ci = FALSE, dcolumn = TRUE, booktabs = TRUE, digits = 3, custom.model.names = c("Hours (more than 20)")) -->
<!-- ``` -->




<!-- --- -->

<!-- ## Moderator analyses [with K, B, se, and p] -->

<!-- ### Decoding -->

<!-- Researcher-Developed vs standardized: -->

<!-- ```{r} -->
<!-- df_d %>% -->
<!--   mutate(custom = if_else(str_detect(type, "^DR"), 1L, 0L)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ custom) -->
<!-- ``` -->


<!-- Stance [0 vs 1/2]: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ stance_0_vs_12) -->
<!-- ``` -->


<!-- Stance [0 (comparison) vs 1 vs 2]: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ factor(stance)) -->
<!-- ``` -->


<!-- Tech vs tech plus: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ t1_tech_techplus) -->
<!-- ``` -->


<!-- Tech type [CAI (base) vs e-reader vs other]: -->

<!-- No "Other" exists on Decoding. -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ t1_tech_type) -->
<!-- ``` -->



<!-- Gamification: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ gamification) -->
<!-- ``` -->

<!-- Adaptive: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_d, method = "REML", mods = ~ adaptive) -->
<!-- ``` -->


<!-- Hours [more than 20]: -->

<!-- ```{r} -->
<!-- df_d %>% -->
<!--   mutate(hours_more_than_20 = if_else(t1_number_of_hours > 20, 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ hours_more_than_20) -->
<!-- ``` -->


<!-- Grouping [1 vs rest combined]: -->

<!-- ```{r} -->
<!-- df_d %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ t1_group_size_more_than_1) -->
<!-- ``` -->



<!-- Grade [K-2 vs 3-5]: -->

<!-- ```{r} -->
<!-- df_d %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ grade) -->
<!-- ``` -->



<!-- Low SES: -->

<!-- ```{r} -->
<!-- df_d %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ low_ses) -->
<!-- ``` -->



<!-- L2+ included: -->

<!-- ```{r} -->
<!-- df_d %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ l2inc) -->
<!-- ``` -->



<!-- Disability: -->

<!-- ```{r} -->
<!-- df_d %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ disabilities_inc) -->
<!-- ``` -->



<!-- QED vs RCT: -->

<!-- ```{r} -->
<!-- df_d %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ design) -->
<!-- ``` -->


<!-- ALT vs BAU: -->

<!-- ```{r} -->
<!-- df_d %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ c1_bau_alt) -->
<!-- ``` -->


<!-- --- -->

<!-- ### Reading Comprehension -->

<!-- Researcher-Developed vs standardized: -->

<!-- ```{r} -->
<!-- df_c %>% -->
<!--   mutate(custom = if_else(str_detect(type, "^CR"), 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ custom) -->
<!-- ``` -->


<!-- Stance [0 vs 1/2]: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ stance_0_vs_12) -->
<!-- ``` -->


<!-- Stance [0 (comparison) vs 1 vs 2]: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ factor(stance)) -->
<!-- ``` -->


<!-- Tech vs tech plus: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ t1_tech_techplus) -->
<!-- ``` -->


<!-- Tech type [CAI (base) vs e-reader vs other]: -->

<!-- No "e-reader" exists for Reading Comprehension. -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ t1_tech_type) -->
<!-- ``` -->


<!-- Gamification: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ gamification) -->
<!-- ``` -->

<!-- Adaptive: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_c, method = "REML", mods = ~ adaptive) -->
<!-- ``` -->


<!-- Hours [more than 20]: -->

<!-- ```{r} -->
<!-- df_c %>% -->
<!--   mutate(hours_more_than_20 = if_else(t1_number_of_hours > 20, 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ hours_more_than_20) -->
<!-- ``` -->


<!-- Grouping [1 vs rest combined]: -->

<!-- ```{r} -->
<!-- df_c %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ t1_group_size_more_than_1) -->
<!-- ``` -->



<!-- Grade [K-2 vs 3-5]: -->

<!-- ```{r} -->
<!-- df_c %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ grade) -->
<!-- ``` -->



<!-- Low SES: -->

<!-- ```{r} -->
<!-- df_c %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ low_ses) -->
<!-- ``` -->



<!-- L2+ model: -->

<!-- ```{r} -->
<!-- df_c %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ l2inc) -->
<!-- ``` -->



<!-- Disability: -->

<!-- ```{r} -->
<!-- df_c %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ disabilities_inc) -->
<!-- ``` -->



<!-- QED vs RCT: -->

<!-- ```{r} -->
<!-- df_c %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ design) -->
<!-- ``` -->


<!-- ALT vs BAU: -->

<!-- ```{r} -->
<!-- df_c %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ c1_bau_alt) -->
<!-- ``` -->



<!-- --- -->


<!-- ### Listening Comprehension -->

<!-- Researcher-Developed vs standardized: -->

<!-- ```{r} -->
<!-- df_l %>% -->
<!--   mutate(custom = if_else(str_detect(type, "^LR"), 1L, 0L)) %>% #tabyl(type, custom) -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ custom) -->
<!-- ``` -->

<!-- Stance [0 vs 1/2]: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ stance_0_vs_12) -->
<!-- ``` -->


<!-- Stance [0 (comparison) vs 1 vs 2]: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ factor(stance)) -->
<!-- ``` -->


<!-- Tech vs tech plus: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ t1_tech_techplus) -->
<!-- ``` -->


<!-- Tech type [CAI (base) vs e-reader vs other]: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ t1_tech_type) -->
<!-- ``` -->



<!-- Gamification: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ gamification) -->
<!-- ``` -->

<!-- Adaptive: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_l, method = "REML", mods = ~ adaptive) -->
<!-- ``` -->


<!-- Hours [more than 20]: -->

<!-- ```{r} -->
<!-- df_l %>% -->
<!--   mutate(hours_more_than_20 = if_else(t1_number_of_hours > 20, 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ hours_more_than_20) -->
<!-- ``` -->


<!-- Grouping [1 vs rest combined]: -->

<!-- ```{r} -->
<!-- df_l %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ t1_group_size_more_than_1) -->
<!-- ``` -->



<!-- Grade [K-2 vs 3-5]: -->

<!-- ```{r} -->
<!-- df_l %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ grade) -->
<!-- ``` -->



<!-- Low SES: -->

<!-- ```{r} -->
<!-- df_l %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ low_ses) -->
<!-- ``` -->



<!-- L2+ model: -->

<!-- ```{r} -->
<!-- df_l %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ l2inc) -->
<!-- ``` -->



<!-- Disability: -->

<!-- ```{r} -->
<!-- df_l %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ disabilities_inc) -->
<!-- ``` -->



<!-- QED vs RCT: -->

<!-- ```{r} -->
<!-- df_l %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ design) -->
<!-- ``` -->


<!-- ALT vs BAU: -->

<!-- ```{r} -->
<!-- df_l %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ c1_bau_alt) -->
<!-- ``` -->


<!-- --- -->

<!-- ### Writing -->

<!-- Researcher-Developed vs standardized: -->

<!-- ```{r} -->
<!-- df_w %>% -->
<!--   mutate(custom = if_else(str_detect(type, "^WPR"), 1L, 0L)) %>% -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ custom) -->
<!-- ``` -->


<!-- Stance [0 vs 1/2]: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ stance_0_vs_12) -->
<!-- ``` -->


<!-- Stance [0 (comparison) vs 1 vs 2]: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ factor(stance)) -->
<!-- ``` -->


<!-- Tech vs tech plus: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ t1_tech_techplus) -->
<!-- ``` -->


<!-- Tech type [CAI (base) vs e-reader vs other]: -->

<!-- No "e-reader" level for Writing. -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ t1_tech_type) -->
<!-- ``` -->


<!-- Gamification: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ gamification) -->
<!-- ``` -->

<!-- Adaptive: -->

<!-- ```{r} -->
<!-- rma(yi = ES, vi = EV, data = df_w, method = "REML", mods = ~ adaptive) -->
<!-- ``` -->


<!-- Hours [more than 20]: -->

<!-- ```{r} -->
<!-- df_w %>% -->
<!--   mutate(hours_more_than_20 = if_else(t1_number_of_hours > 20, 1L, 0L)) %>%  -->
<!--   rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ hours_more_than_20) -->
<!-- ``` -->


<!-- Grouping [1 vs rest combined]: -->

<!-- ```{r} -->
<!-- df_w %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ t1_group_size_more_than_1) -->
<!-- ``` -->



<!-- Grade [K-2 vs 3-5]: -->

<!-- ```{r} -->
<!-- df_w %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ grade) -->
<!-- ``` -->



<!-- Low SES: -->

<!-- ```{r} -->
<!-- df_w %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ low_ses) -->
<!-- ``` -->



<!-- L2+ model: -->

<!-- ```{r} -->
<!-- df_w %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ l2inc) -->
<!-- ``` -->



<!-- Disability: -->

<!-- ```{r} -->
<!-- df_w %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ disabilities_inc) -->
<!-- ``` -->



<!-- QED vs RCT: -->

<!-- ```{r} -->
<!-- df_w %>% rma(yi = ES, vi = EV, data = ., method = "REML", mods = ~ design) -->
<!-- ``` -->


<!-- ALT vs BAU: No variation in data along levels -->



<!-- --- -->


<!-- ## Publication Bias -->

<!-- ### Funnel Plots -->

<!-- Decoding (Constrained skills): -->


<!-- ```{r, fig.retina=4} -->
<!-- df_d %>% -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     mods = ~ type, -->
<!--     method = "REML" -->
<!--   ) %>% -->
<!--   funnel(xlab = "Constrained Skills Effect Size", pch = 21, bg = "grey") -->
<!-- ``` -->


<!-- Reading Comprehension: -->

<!-- ```{r, fig.retina=4} -->
<!-- df_c %>% -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     mods = ~ type, -->
<!--     method = "REML" -->
<!--   ) %>% -->
<!--   funnel(xlab = "Reading Comprehension Effect Size", pch = 21, bg = "grey") -->
<!-- ``` -->

<!-- Language Comprehension (Unconstrained skills): -->


<!-- ```{r, fig.retina=4} -->
<!-- df_l %>% -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     mods = ~ type, -->
<!--     method = "REML" -->
<!--   ) %>% -->
<!--   funnel(xlab = "Unconstrained Skills Effect Size", pch = 21, bg = "grey") -->
<!-- ``` -->

<!-- Writing: -->


<!-- ```{r, fig.retina=4} -->
<!-- df_w %>% -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     mods = ~ type, -->
<!--     method = "REML" -->
<!--   ) %>% -->
<!--   funnel(xlab = "Writing Effect Size", pch = 21, bg = "grey") -->
<!-- ``` -->

<!-- ### Egger's Tests -->

<!-- Decoding (Constrained skills): -->

<!-- ```{r} -->
<!-- df_d %>% -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     mods = ~ type, -->
<!--     method = "REML" -->
<!--   ) %>% -->
<!--   regtest(model = "rma", predictor = "sei") -->
<!-- ``` -->

<!-- Reading Comprehension: -->

<!-- ```{r} -->
<!-- df_c %>% -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     mods = ~ type, -->
<!--     method = "REML" -->
<!--   ) %>% -->
<!--   regtest(model = "rma", predictor = "sei") -->
<!-- ``` -->

<!-- Language Comprehension (Unconstrained skills): -->

<!-- ```{r} -->
<!-- df_l %>% -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     mods = ~ type, -->
<!--     method = "REML" -->
<!--   ) %>% -->
<!--   regtest(model = "rma", predictor = "sei") -->
<!-- ``` -->

<!-- Writing: -->

<!-- ```{r} -->
<!-- df_w %>% -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     mods = ~ type, -->
<!--     method = "REML" -->
<!--   ) %>% -->
<!--   regtest(model = "rma", predictor = "sei") -->
<!-- ``` -->

<!-- ### P-curves -->

<!-- Decoding (Constrained skills): -->

<!-- ```{r} -->
<!-- df_d %>%  -->
<!--   mutate( -->
<!--     SE = sqrt(EV) -->
<!--   ) %>%  -->
<!--   meta::metagen( -->
<!--     ES, -->
<!--     SE, -->
<!--     data = ., -->
<!--     comb.fixed = F, -->
<!--     comb.random = T, -->
<!--     method.tau = "REML", -->
<!--     hakn = T, -->
<!--     sm = "SMD" -->
<!--   ) %>%  -->
<!--   pcurve() -->
<!-- ``` -->

<!-- Reading Comprehension: -->

<!-- ```{r} -->
<!-- df_c %>%  -->
<!--   mutate( -->
<!--     SE = sqrt(EV) -->
<!--   ) %>%  -->
<!--   meta::metagen( -->
<!--     ES, -->
<!--     SE, -->
<!--     data = ., -->
<!--     comb.fixed = F, -->
<!--     comb.random = T, -->
<!--     method.tau = "REML", -->
<!--     hakn = T, -->
<!--     sm = "SMD" -->
<!--   ) %>%  -->
<!--   pcurve() -->
<!-- ``` -->

<!-- Language Comprehension (Unconstrained skills): -->

<!-- ```{r} -->
<!-- df_l %>%  -->
<!--   mutate( -->
<!--     SE = sqrt(EV) -->
<!--   ) %>%  -->
<!--   meta::metagen( -->
<!--     ES, -->
<!--     SE, -->
<!--     data = ., -->
<!--     comb.fixed = F, -->
<!--     comb.random = T, -->
<!--     method.tau = "REML", -->
<!--     hakn = T, -->
<!--     sm = "SMD" -->
<!--   ) %>%  -->
<!--   pcurve() -->
<!-- ``` -->

<!-- Writing: -->

<!-- ```{r} -->
<!-- df_w %>%  -->
<!--   mutate( -->
<!--     SE = sqrt(EV) -->
<!--   ) %>%  -->
<!--   meta::metagen( -->
<!--     ES, -->
<!--     SE, -->
<!--     data = ., -->
<!--     comb.fixed = F, -->
<!--     comb.random = T, -->
<!--     method.tau = "REML", -->
<!--     hakn = T, -->
<!--     sm = "SMD" -->
<!--   ) %>%  -->
<!--   pcurve() -->
<!-- ``` -->


<!-- --- -->


<!-- ## Sensitivity analyses -->

<!-- ### Exclude high selection risk studies [Keep RCTs only] -->


<!-- Decoding (Constrained skills): -->

<!-- ```{r} -->
<!-- df_d %>% -->
<!--   filter(design == "RCT") %>%  -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     method = "REML" -->
<!--   ) -->
<!-- ``` -->


<!-- Reading Comprehension: -->

<!-- ```{r} -->
<!-- df_c %>% -->
<!--   filter(design == "RCT") %>%  -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     method = "REML" -->
<!--   ) -->
<!-- ``` -->



<!-- Language Comprehension (Unconstrained skills): -->


<!-- ```{r} -->
<!-- df_l %>% -->
<!--   filter(design == "RCT") %>%  -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     method = "REML" -->
<!--   ) -->
<!-- ``` -->


<!-- Writing: -->


<!-- ```{r} -->
<!-- df_w %>% -->
<!--   filter(design == "RCT") %>%  -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     method = "REML" -->
<!--   ) -->
<!-- ``` -->


<!-- --- -->

<!-- ### Constrain outliers by Winsorizing -->

<!-- Decoding (Constrained skills): -->

<!-- ```{r} -->
<!-- df_d %>% -->
<!--   mutate( -->
<!--     ES = DescTools::Winsorize(ES) -->
<!--   ) %>%  -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     method = "REML" -->
<!--   ) -->
<!-- ``` -->



<!-- Reading Comprehension: -->

<!-- ```{r} -->
<!-- df_c %>% -->
<!--   mutate( -->
<!--     ES = DescTools::Winsorize(ES) -->
<!--   ) %>%   -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     method = "REML" -->
<!--   ) -->
<!-- ``` -->



<!-- Language Comprehension (Unconstrained skills): -->


<!-- ```{r} -->
<!-- df_l %>% -->
<!--   mutate( -->
<!--     ES = DescTools::Winsorize(ES) -->
<!--   ) %>%  -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     method = "REML" -->
<!--   ) -->
<!-- ``` -->



<!-- Writing: -->


<!-- ```{r} -->
<!-- df_w %>% -->
<!--   mutate( -->
<!--     ES = DescTools::Winsorize(ES) -->
<!--   ) %>%  -->
<!--   rma( -->
<!--     yi = ES,  -->
<!--     vi = EV,  -->
<!--     data = .,  -->
<!--     method = "REML" -->
<!--   ) -->
<!-- ``` -->

<!-- --- -->

<!-- ### Changing within study correlations (when aggregating effect sizes within a study) -->

<!-- Decoding (Constrained skills): -->

<!-- ```{r} -->
<!-- df_append %>%  -->
<!--   filter(str_detect(type, "^D")) %>% -->
<!--   robu( -->
<!--     formula = ES ~ 1,  -->
<!--     var.eff.size = EV,  -->
<!--     studynum = stdid, -->
<!--     data = .,  -->
<!--     modelweights = "CORR" -->
<!--     ) %>%  -->
<!--   sensitivity() -->
<!-- ``` -->


<!-- Reading Comprehension: -->

<!-- ```{r} -->
<!-- df_append %>%  -->
<!--   filter(str_detect(type, "^C")) %>% -->
<!--   robu( -->
<!--     formula = ES ~ 1,  -->
<!--     var.eff.size = EV,  -->
<!--     studynum = stdid, -->
<!--     data = .,  -->
<!--     modelweights = "CORR" -->
<!--     ) %>%  -->
<!--   sensitivity() -->
<!-- ``` -->


<!-- Listening Comprehension (Unconstrained skills): -->

<!-- ```{r} -->
<!-- df_append %>%  -->
<!--   filter(str_detect(type, "^L")) %>% -->
<!--   robu( -->
<!--     formula = ES ~ 1,  -->
<!--     var.eff.size = EV,  -->
<!--     studynum = stdid, -->
<!--     data = .,  -->
<!--     modelweights = "CORR" -->
<!--     ) %>%  -->
<!--   sensitivity() -->
<!-- ``` -->


<!-- Writing: -->

<!-- ```{r} -->
<!-- df_append %>%  -->
<!--   filter(str_detect(type, "^W")) %>% -->
<!--   robu( -->
<!--     formula = ES ~ 1,  -->
<!--     var.eff.size = EV,  -->
<!--     studynum = stdid, -->
<!--     data = .,  -->
<!--     modelweights = "CORR" -->
<!--     ) %>%  -->
<!--   sensitivity() -->
<!-- ``` -->




